Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-03-28 paper.tex
Comment out figure for now
Add citation for Re-dependence of dynamic stall
Update Re table

@@

\begin{table}
\centering
\begin{tabular}{ccc}
Tow speed (m/s) & $Re_D$ & $Re_c$ ($\lambda = 1.9$) \\ 
\hline
0.2 & $2.0 \times 10^5$ &  \\ 
0.4 & $4.0 \times 10^5$ &  \\ 
0.6 & $6.0 \times 10^5$ &  \\ 
0.8 & $8.0 \times 10^5$ &  \\ 
1.0 & $1.0 \times 10^6$ &  \\ 
1.2 & $1.2 \times 10^6$ &  \\ 
\end{tabular} 
\caption{Turbine diameter and approximate blade chord Reynolds numbers for the
tow speeds at which full performance curves and wake maps were measured.}
\label{tab:Re}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/turbine_coordinate_system}
\caption{Wake measurement coordinate system and locations. Dimensions are in
meters.} 
\label{fig:wake_locations}
\end{figure}

>>>>

Bousman showed that dynamic stall was insensitive to Reynolds number for $Re=1.0
\times 10^5$--$2.5 \times 10^5$ \cite{Bousman2000-evaluation}.

@@

\begin{table}
\centering
\begin{tabular}{ccc}
Tow speed (m/s) & $Re_D$ & $Re_{c,\mathrm{ave}}$ ($\lambda = 1.9$) \\ 
\hline
0.3 & $3.0 \times 10^5$ & $8.0 \times 10^4$ \\ 
0.4 & $4.0 \times 10^5$ & $1.1 \times 10^5$ \\ 
0.5 & $5.0 \times 10^5$ & $1.3 \times 10^5$ \\ 
0.6 & $6.0 \times 10^5$ & $1.6 \times 10^5$ \\ 
0.7 & $7.0 \times 10^5$ & $1.9 \times 10^5$ \\ 
0.8 & $0.8 \times 10^5$ & $2.1 \times 10^5$ \\ 
0.9 & $0.9 \times 10^5$ & $2.4 \times 10^5$ \\ 
1.0 & $1.0 \times 10^6$ & $2.7 \times 10^5$ \\ 
1.1 & $1.1 \times 10^6$ & $2.9 \times 10^5$ \\ 
1.2 & $1.2 \times 10^6$ & $3.2 \times 10^5$ \\ 
1.3 & $1.3 \times 10^6$ & $3.4 \times 10^5$ \\ 
\end{tabular} 
\caption{Turbine diameter and approximate blade chord Reynolds numbers for the
tow speeds used in the experiment.}
\label{tab:Re}
\end{table}

@@

\begin{figure}
\centering
%\includegraphics[width=0.9\textwidth]{figures/turbine_coordinate_system}
\caption{Wake measurement coordinate system and locations. Dimensions are in
meters.} 
\label{fig:wake_locations}
\end{figure}
